Figures

### 2019-04-16 code/figures.rmd
Fixed code for tau2 density plot

```{r Density_plot, fig.asp= 0.618, cache = TRUE}

@@

# dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
# names(dens_tau2) <-  sort(unique(dat$effect))
# 
# #Simulated data at various heterogeneity levels, prep for plotting
# tau2_dist <- dens_tau2 %>% 
#   bind_rows(.id = "effect") %>% 
#   rename(Heterogeneity = tau_index) %>% 
#   mutate(Heterogeneity = recode(Heterogeneity,
#                             '1' = "Zero",
#                             '2' = "Small",
#                             '3' = "Medium",
#                             '4' = "Large"),
#          Heterogeneity = as.factor(Heterogeneity))
# 
# #Observed tau22 estimates, i.e, results from main table, see table.rmd
# #Effects estimated with sourced function 'summarizer'
# observed <- dat %>% 
#   split(.$effect) %>%  
#   map_dfr(summarizer, .id = "effect") %>% 
#   select(effect, tau2 = tau2) %>%
#   mutate(Heterogeneity = "Observed")
# 
# tau2_plot <- ggplot(tau2_dist, aes(x = tau2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
#   geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
#   geom_density(alpha = 0.3) +
#   theme_classic() +
#   coord_cartesian(xlim = c(0, 100))  +
#   scale_fill_brewer(palette = "Dark2",
#                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
#                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
#   scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
#                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
#                         labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
#   scale_color_brewer(palette = "Dark2", 
#                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
#                      labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
#   theme(legend.position = c(0.85, 0.71),
#         legend.background = element_rect(linetype = "solid", color = "black")) +
#   scale_y_continuous(name = "Density") +
#   scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
#   guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
# 
# #ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
# 
# #3) combine I2-tau2-density-plots----
# 
# densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
# densities
# #save_plot("../figures/densities_het.png", densities,
# #          nrow = 2, base_height = 5, base_width = 5, dpi = 600)

>>>>

```{r Density_plot, cache = TRUE}

@@

dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
names(dens_tau2) <-  sort(unique(dat$effect))

# Simulated data at various heterogeneity levels, prep for plotting
tau2_dist <- dens_tau2 %>%
 bind_rows(.id = "effect") %>%
 rename(Heterogeneity = tau_index) %>%
 mutate(Heterogeneity = recode(Heterogeneity,
                             '1' = "Zero",
                             '2' = "Small",
                             '3' = "Medium",
                             '4' = "Large"),
          Heterogeneity = as.factor(Heterogeneity))

# Observed tau22 estimates, i.e, results from main table, see table.rmd
# Effects transformed and estimated with sourced functions 'transform_MA' and 'summarizer'
observed_tau2 <- dat %>%
   split(.$effect) %>%
   map(transform_MA) %>% 
   map_dfr(summarizer, .id = "effect") %>%
   select(effect, tau2) %>%
   mutate(Heterogeneity = "Observed")

tau2_plot <- ggplot(tau2_dist, aes(x = tau2_hat, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed_tau2, aes(y = ..density.., x = tau2), bins = 200, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 0.05)) +
  scale_fill_brewer(palette = "Dark2",
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                         labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  scale_color_brewer(palette = "Dark2",
                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                      labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
       legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

#ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())

#3) combine I2-tau2-density-plots----
densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
densities

# save_plot("../figures/densities_het.png", densities,
     #      nrow = 2, base_height = 5, base_width = 5, dpi = 600)
```
